{\em pyg4ometry}, a python library for the creation of Monte Carlo particle transport geometries

### 2019-02-14 paper/pyg4ometry.tex

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

@@

\section{Geometric descriptions} \label{sec:geometric}

@@

\subsection{Boundary representation (BREP)}
Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices.

\subsection{Tessellated polygons}
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL.

\subsection{Geant4 geometery}
Geant4 geometry description is a mixture of BREP and CSG concepts. Geant4 includes XX fundamental solids, although it does not store a sense of topology
present in traditional CAD BREP systems. Geant4 also provides the ability to perform boolean operations on these primitive solids.

@@

\section{Rapid geometry modelling in Python}

\section{Conversion to Geant4 from common CAD formats}

\section{Conversion between Geant4 and FLUKA}

>>>>

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compres ses without sorting
%%
%% \biboptions{comma,round}

@@

\section{Geometric descriptions} \label{sec:geometric}
Central to description of a geometric description of a system is how a solid is defined in three dimensions. There are numerous different ways to describe a
geometry and these are described briefly in the following sections.

@@

\subsection{Boundary representation (BREP)}
Boundary representation consists of two parts, topology and geometry. Topological elements are faces, edges and vertices. No current PT applications use native 
file formats employed by CAD systems. The conversion of CAD BREP formats for loading in PT applications is typically performed via a tessellated format.

\subsection{Tessellated polygons}
Solid volumes can be defined using triangular, quadrilateral or tetrahedral meshes. Numerous formats exist to describe meshes, the ubiquitous being STL and more 
modern variants being PLY, OBJ, etc.

\subsection{Geant4 geometery}
Geant4 geometry description is a mixture of BREP, CSG and tessellated concepts. Geant4 includes XX fundamental solids, although it does not store a sense 
of topology present in traditional CAD BREP systems. One of the fundamental solids is a {\em TessellatedSolid} which can used to represent STL or PLY files. 
Geant4 also provides the ability to perform boolean operations on these primitive solids. The richest and most flexible geometry description is currently used by
Geant4. Not only do solid objects need to be defined but also placed in a world coordinate system. Geant4 has two concepts which facilitate this {\it Logical Volumes} 
and {\it Physical Volumes}. A Logical Volume is a volume that has an outer solid but also material, magnetic field and zero or more physical {\it daughter} volumes. A Physical 
Volume is a placement (or instance) of a Logical Volume.

@@

\section{Rapid geometry modelling}

\section{CAD to Geant4 conversion }

\section{Geant4 and FLUKA conversion}
